---
output:
  word_document: default
  html_document: default
---
-----
title: "CE-QUAL-W2 temperature modeling of Willamette Reservoirs"
author: Norman Buccola
output: html_document
----

```{r global_options, include=FALSE,results="hide"} 
# Norman Buccola, USACE, 2023-07-26
# the First time you run this script you may need to install the following packages
#install.packages('devtools')
#devtools::install_github("nbuccola/w2r") 

#install.packages(c('reshape2','foreach','lubridate','ggplot2','plyr','RColorBrewer','scales','hydroTSM'))
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=8, fig.height=4, fig.path='Figs/',                      #root.dir='/media/removable/Elements/ColumbiaEIS/',
                      #root.dir='F:/ColumbiaEIS/',
                      include=T,echo=F, warning=FALSE,message=FALSE)
library(foreach)
library(xts); 
library(gdata); library(reshape2); 
library(ggplot2)
library(scales)
library(RColorBrewer)
library(tidyr)
library(lubridate)
library(dplyr)
library(readr)
library(w2r)
#ls("package:w2r")

c2f<-function(x) {(x*(9/5))+32}
f2c<-function(x) {(x-32)*(5/9)}

# Set working directory
wd<-"C:/Users/g2echnb9/Documents/WillametteDisposition2023"
DataDir <- file.path(wd,'RES-SIM')
projFldr<-'DcmPnstck'
# Where to get RES-SIM data
RefDataDir<-file.path(wd,'RefData') # 
#funcDir <- 'C:/Users/g2echnb9/Documents/R/w2r/R'
verDir<-''
scenarios<-data.frame(Baseline = NA,DcmPnstck = NA,RcnPnstck = NA,StationService = NA)

years<-c('2011','2015','2016')
# Read in RES-SIM to W2 codes
RessimCodes<-read.csv(file.path(DataDir,'WillW2OutputNmsSeg.csv'),stringsAsFactors = F)
# Load outlets at each dam
source(file.path(DataDir,'QGT_elvsFrom_w2_con_2021-11-01.r'))

# Load the Rule Curves
source(file.path(DataDir,'WVWQfunctions_2023-07-19.r'))

RuleCurveDir <- file.path(RefDataDir,'rule_curves')
rcs <- ReadRuleCurves(RuleCurveDir) %>% 
   expand_grid(tibble(Year = c('2011','2015', '2016')))  %>%
   expand_grid(tibble(Alt = names(scenarios))) %>%
   mutate(Year = as.factor(Year)) #,
          # Site = as.factor(Site,levels =  names(qgtConfig$CenterElvs),ordered=T)) 
rcs$Site <- as.factor(rcs$Site)

elvVolCurvPath <- file.path(RefDataDir,'elv_vol_curves')


```

Water Balance steps:
1) Run the W2 models a first time with QDT set to OFF. 
2) Run the following code chunk to calculate the missing flow needed (QDT) to meet the operational lake levels and close the water balance for each reservoir. Use the WillW2_HCR-LOP_IRRM_2020_watbalSwitch.csv file to control which reservoir, year, and scenario needs a new QDT (re-)written. 
3) Re-Run W2 model with QDT set to ON and repeat step 2. 
4) Repeat steps 2 and 3 as needed. In the MF Willamette, only one iteration was needed.


```{r RunWaterBalance, echo=F,include =F,results="hide"}
rm(wbFits)
firstRun<-F # True will change QDT to "OFF" in the control file
watbalSwitches<-read.csv(file.path(wd,'WillW2_HydDisp_watbalSwitch.csv'),stringsAsFactors = F,header=T)
watbalSwitches <- watbalSwitches[colSums(!is.na(watbalSwitches)) > 0] %>% drop_na()
watbalSwitchesBig <- merge(watbalSwitches,RessimCodes,by = 'RESSIMCode',all = T)
wbFits<-as.list(rep(NA,ncol(watbalSwitches)-2)) 
names(wbFits)<-colnames(watbalSwitches)[-c(1,ncol(watbalSwitches))]

for(sc in 1:length(wbFits)){# Loop through scenarios
  #sc=1
  scName <- names(wbFits)[sc]
  print(scName)
  scModWhich<-which(!is.na(watbalSwitchesBig[,sc+1]))
  if(!any(scModWhich)){next} # No models run for this scenario
  resSc <- watbalSwitchesBig[scModWhich,'W2name']
  w2Path<-file.path(wd,scName,resSc)
  w2Dirs<-list.dirs(w2Path,recursive=F)
  w2DirsShrt<-list.dirs(w2Path,recursive=F,full.names = F)
  watbalSc <- watbalSwitchesBig[scModWhich,]
  scDirs <- w2DirsShrt[grep(unique(watbalSc$Year),w2DirsShrt)]
  scMod <- sort(unlist(sapply(unique(watbalSc$W2name),grep,scDirs)))
  scModYrs <- unique(watbalSc$Year)
  #scMods <- sort(unlist(sapply(paste0(watbalSc$W2name,watbalSc$Year),grep,w2DirsShrt)))
  scMods <- grep(scModYrs,w2DirsShrt)
  wbSite<-unique(watbalSc$RESSIMCode)
  scModsDf<-foreach(yr= scModYrs,.combine='rbind') %do% {
    foreach(site= 1:length(wbSite),.combine='rbind') %do% {
      SitePth <- which(grepl(yr,w2DirsShrt) & 
                         grepl(watbalSc$W2name[site],w2DirsShrt))
      if(length(SitePth)>1){SitePth <- SitePth[watbalSc$wb[site]]}
      yrdf <- data.frame(RESSIMCode=wbSite[site],
                         Path = w2Dirs[SitePth],
                         Dir=w2DirsShrt[SitePth],
                       stringsAsFactors = F)
      rcdm <- which(RessimCodes$RESSIMCode %in% yrdf$RESSIMCode)
      #mm$RESSIMCode <- 
      yrdf$SegmentOutput<-RessimCodes$SegmentOutput[rcdm]
      yrdf$wb<-RessimCodes$wb[rcdm]
      return(yrdf)  
    }
  }
  scModsDfsc<-scModsDf
  scModsDfsc$Scenario<-names(wbFits)[sc]
  wbFits[[sc]]<-as.list(w2DirsShrt[scMods]) #rep(NA,length(scMods)))
  names(wbFits[[sc]])<-w2DirsShrt[scMods]
  opt2keep<-c('pre.opt','*.exe',paste0("_seg",unique(scModsDf$SegmentOutput),'.opt'), #'wl.opt',
            paste0("qwo_",unique(scModsDf$SegmentOutput),'.opt'))
  
  for(i in 1:length(scMods)){
    #i=1
    print(scModsDf[i,])
    mod<-scModsDf$RESSIMCode[i]
    wtbli<-grepl(mod,watbalSc$RESSIMCode) & 
      grepl(as.numeric(gsub("\\D","",scModsDf$Dir[i])),
            watbalSc$Year)
    
    # source(file.path(funcDir,'errs.r'))
    # source(file.path(funcDir,'apply.davg.oncols.r'))
    # source(file.path(funcDir,'modifyInitWSELVbth.r'))
    # source(file.path(funcDir,'modifyW2con.r'))
    # source(file.path(funcDir,'moving.avg.r'))
    if(firstRun & watbalSc[wtbli,sc+1]){
      # Change QDT to "OFF"
      qdt<-'OFF'
    }else{
      qdt<-'ON'
    }
    modifyW2con(path=scModsDf$Path[i],
                seg=scModsDf$SegmentOutput[i],
                qdt=qdt,
                wb=scModsDf$wb[i]
                )
  
    # source(file.path(funcDir,'readW2ConInOut.r'))
    # source(file.path(funcDir,'waterBalanceGeneric.r'))
    elvcrvs <- list.files(elvVolCurvPath)
    elvcrv <- elvcrvs[grepl(scModsDf$RESSIMCode[i],elvcrvs)]

    wbFits[[sc]][[i]]<-readW2ConInOut(
      path=scModsDf$Path[i],
      write.files=watbalSc[wtbli,sc+1],
      seg=scModsDf$SegmentOutput[i],
      wb=scModsDf$wb[i],
      elvVolCrvFl = file.path(elvVolCurvPath,elvcrv),
      RESSIMCode=RessimCodes$ReachName[grep(scModsDf$RESSIMCode[i],RessimCodes$RESSIMCode)],
      wd=wd)
    
    # if(watbalSc[wtbli,sc+1]){
    #   # Remove old model output
    #   optfls<-list.files(file.path(w2Path,scModsDf$Dir[i]),pattern='.opt',full.names = T)
    #   opt2keepi<-opt2keep[!grepl(scModsDf$SegmentOutput[i],opt2keep)]
    #   optfls<-optfls[!grepl(paste(opt2keepi,collapse = '|'),optfls)]
    #   for(fl in 1:length(optfls)){
    #       print(paste('Deleting', optfls[fl]))
    #       file.remove(optfls[fl])
    #   }
    # }

    wbFitSc<-data.frame(Scenario=names(scenarios)[sc],
                        Year=watbalSc$Year[wtbli],
                        RESSIMCode=scModsDf$RESSIMCode[i],
                        wbFits[[sc]][[i]]$watbal$fit)
    
    if(exists('wbFitsAll')){
      wbFitsAll<-rbind(wbFitsAll,wbFitSc)
    }else{
      wbFitsAll<-wbFitSc
    }

  }# End Scenario loop

}


wbFitsAll$Year<-as.factor(wbFitsAll$Year)
wbFitsAll$RESSIMCode<-as.factor(wbFitsAll$RESSIMCode)
wbFitsAll$Scenario<-as.factor(wbFitsAll$Scenario)
plt<-ggplot(wbFitsAll[,-match(c('N','ME'),colnames(wbFitsAll))],
       aes(x=RESSIMCode,y=MAE,colour=Year)) +
  geom_point() +
  ggtitle('Water Balance') +
  facet_free(Scenario ~Year,scales = 'fixed')
plt

ggsave(plt,width = 9,height = 6,
       filename = file.path(wd,projFldr,verDir,'WaterBalanceSummary.png'),
       device = 'png')
#save(scModsDf,wbFits,w2io,
#     file=file.path(wd,projFldr,verDir,'MFWill_IRRM_WaterBalanceResults.rdata'))
    
```



