---
output: html_document
---
-----
title: "Compare Willamette Hydropower Disposition Scenarios"
author: Norman Buccola (norman.buccola@usace.army.mil)
output: html_document
----

=====


Purpose/Background
------------

Steps for analyzing scenarios:

1) Post-process RES-SIM output for W2 inputs: Extract 2011, 2015, and 2016 generating gate outflow files (QGT), water surfaces for each project.

2) Post-process RES-SIM output for TDG calculations: Use entire period of record and prepare gate outflow data for TDG python script. 

3) Run TDG python scripts, then post-process here and generate charts, tables.

4) Run W2 water balances using another R script

5) Post-process W2 output here and generate charts, tables.


```{r global_options, include=FALSE,results="hide"} 
library(knitr)
knitr::opts_chunk$set(fig.width=8, fig.height=4, fig.path='Figs/',
                      #root.dir='/media/removable/Elements/ColumbiaEIS/',
                      #root.dir='F:/ColumbiaEIS/',
                      include=T,echo=F, warning=FALSE, message=FALSE)
```


```{r GetInOutKey, echo=F}
# Norman Buccola, USACE, 2023-07-19
#install.packages(c('reshape2','foreach','lubridate','ggplot2','plyr','RColorBrewer','scales','hydroTSM'))

rm(list=ls())

# Load previous w2 model results
#load(file.path(dataDir,"analysis/NAA_Alt1_Alt2a_Alt2b_Alt3a_Alt3b_Alt4_Alt5","WVEIS_WQCompareNAAtoAlt5_2022-08-10.RData"))
wd<-'C:/Users/g2echnb9/Documents'
funcDir<-file.path(wd,'WillametteDisposition2023/RES-SIM')
dataDir<-file.path(wd,'WillametteDisposition2023/RES-SIM') # Where to get RES-SIM data
RefDataDir<-file.path(wd,'WillametteDisposition2023/RefData') # 
writeDir<-file.path(wd,'WillametteDisposition2023/analysis')

# source(file.path(funcDir,'makeW2.input.file.r'))
# source(file.path(funcDir,'temp.est.funcs.r'))
# source(file.path(funcDir,'get.w2.inflows.r'))
# source(file.path(funcDir,'moving.avg.r'))
# source(file.path(funcDir,'read.interp.davg.r'))
source(file.path(funcDir,'WVEIS_w2ConQIN_rows.r'))
# Load Colors
source(file.path(funcDir,'colorPal.R')) # Need to replace 'eis.pal' with 'MyPal'
library(reshape2)
library(foreach)
library(lubridate)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(scales)
library(hydroTSM)
library(readxl)
#library(plotly)
library(readr)
library(tidyr)
library(dplyr)
library(purrr)
#devtools::install_github("nbuccola/w2r",force=T)
library(w2r)

#library(dssrip)
cfs2cms<- 1/35.31466688252347 
ft2m<-1/3.28084
c2f <-function(x){x*(9/5)+32} # convert to F
f2c <-function(x){(x-32)*(5/9)} # convert to C
mnthdys<-c("03-15","04-01","04-15","05-01","05-15","06-01","06-15","07-01","07-15","08-01","08-15","09-01")

mnthdysAll<-c("01-01","01-15","02-01","02-15","03-01",mnthdys,"09-15","10-01","10-15","11-01","11-15","12-01","12-15")
spawndays <- c(244,263,274)
Sts3ltr <- c("HCR","LOP","DEX","CGR","GPR","FOS" ,"DET","BCL") #,"ALB","SLM"
StsCWMS <- c("HCRO","DEXO","CGRO","GPRO","SSFO","BCLO")
StsCWMSall <- c(StsCWMS,"ALBO", "SLMO")
Sts2Smrz<-paste(StsCWMSall,collapse = '|') 
#Sts2SmrzLow <- "JASO|VIDO|NSJO|JFFO|HARO|ALBO|SLMO"
Sts2SmrzLow <- "ALBO|SLMO"

#Sts2Smrz<-paste(c('Niagara','Foster','Rainbow','Dexter','Albany','Keizer'),collapse = '|') 
    
#summarize to bi-monthly increments
p <- c(0.05, 0.5, 0.95)
p_names <- map_chr(p, ~paste0(.x*100, "%"))
p_funs <- map(p, ~partial(function(x){round(quantile(x, probs = .x, na.rm = TRUE),1)})) %>% 
  set_names(nm = p_names)
p_funs[['nDaysAbv110']] <- function(x){length(which(x>110))}
statLabs <- c(paste0("TDG ",names(p_funs)[c(1:3)]),"nDaysAbv110")
names(statLabs) <- names(p_funs)
w2dir <- file.path(wd,'WillametteDisposition2023') #,'WQ')
w2TtargDir <- file.path(RefDataDir,'W2TempTargets_2021-01-19')
WSELVobsDir <- file.path(RefDataDir,'WVP_WSELV_2011-2016')
tobsDir <- file.path(RefDataDir,'measured')
#Sts<-c("HCRO","DEXO","CGRO","SSFO" ,"BCLO") #"GPRO",
source(file.path(funcDir,'WVWQfunctions.r'))
# Read in proposed temp targets for action alternatives (AA)
tts <- ReadW2Targs(w2TtargDir)
# Read in ODEQ TMDL temp targets
TMDLtargdir <- file.path(RefDataDir,'TMDL_TempTargs')
# Should be 13, 16, and 18 deg C
ttTMDL <- ReadTMDLTargs(TMDLtargdir)

ORStnd <- ReadOrStStnds(TMDLtargdir = gsub('TMDL_TempTargs','DEQ_ORStStndrds',TMDLtargdir))

# Read in RA targets as of 2023-02-02 (many from 2008 BiOP)
RATargsdir <- file.path(RefDataDir,'WilTempTargsCWMS.csv')
ttRA <- ReadRATargs(RATargsdir)
ttAll <- bind_rows(tts,ttTMDL,ttRA,ORStnd) %>%
  mutate(ttType = as.factor(ttType),
         Location = factor(Location,ordered=T,
                           levels = Sts3ltr)) #'GPR',
rm(tts,ttTMDL,ttRA,ORStnd)

# Define names  of DSS files
altDirs<-list(Measured = list(w2dir = NA),
              Baseline = list(
                fld = file.path(dataDir,'Baseline'),
                dss = 'DISP23_MGO0_14Sep2023_220326.dss',
                partF=c('DISP23_MGO0'),
                w2dir = file.path(w2dir,'Baseline')),
              StnSrvc = list(
                fld = file.path(dataDir,'StationService'),
                dss = 'STA_SERV--0_15Sep2023_083002.dss',
                partF=c('STA_SERV--0'),
                w2dir = file.path(w2dir,'ChangeThis')),
              DcmPenstock = list(
                fld = file.path(dataDir,'NoPenstock'),
                dss = 'NO_PP_MGO-0_15Sep2023_083002.dss',
                partF=c('NO_PP_MGO-0'),
                w2dir = file.path(w2dir,'DcmPenstock'))
              )
altDirs[['Measured']] <- NULL
# altDirs[['Baseline']] <- NULL
# altDirs[['DcmPenstock']] <- NULL
# altDirs[['StnSrvc']] <- NULL

# Define names of DSS files
#ExcCrit <- read_xlsx(file.path(dataDir,'analysis/TempEvaluationCriteriaKoch2020.xlsx'),sheet = 1)

usace_gagenms <- read_xlsx(file.path(RefDataDir,'WVEISGages.xlsx')) %>%
  mutate(Gage = as.character(Gage)) %>%
  distinct()
 
EIS_outputlocs <- read_csv(file.path(RefDataDir,'EIS_outputlocs.csv')) %>% 
  filter(Temp) %>%
  inner_join(usace_gagenms %>% select(Gage,USACE_ID), by = 'Gage') %>%
  select(c(Model,River,Gage,`Gage Name`,`Will_RM-midpt`,'USACE_ID')) %>%
  distinct()
rm(usace_gagenms)


source(file.path(funcDir,'makeQGT4WillW2_2022-12-12.r'))
compDir <- file.path(writeDir,paste0(names(altDirs),collapse = '_'))
dir.create(compDir)

source(file.path(dataDir,'QGT_elvsFrom_w2_con_2021-11-01.r'))
# Define names of DSS files

altDirs <- lapply(altDirs,function(x){
  x[['RoptFlNm']] <- paste0(gsub('.dss','',x[['dss']]),'_TDGnpts.Rdata')
  x[['RTDGoptFlNm']] <- file.path('TDG_Analysis','BasePrcOutage',gsub('TDGnpts','TDGotpts4AltCmp',x[['RoptFlNm']]))
  x[['RW2nptsFlNm']] <- paste0(gsub('.dss','',x[['dss']]),'_W2inputs.Rdata')
 return(x)}
  ) 

library("scales")
library('ggsci')

# ImpactPal <- show_col(pal_futurama("planetexpress", alpha = 0.6)(12))

ImpactPal <- c(`Major Adv`="#6C4C40FF",`Moderate Adv` = "#8C6D63FF", #Browns
               `Minor Adv`="#BBAAA4FF",
               `Negligible` = "#3F404199", 
               `Minor Ben` =  "#BADEFAFF",# Blues
               `Moderate Ben`="#64B4F6FF",`Major Ben`="#2096F2FF" ) 

```

```{r CompareOpsInW2Years, echo=F}
source(file.path(funcDir,'WVWQfunctions.r'))
#Read summary of Ops data in W2 model years
w2npts <- foreach(alt= 1:length(altDirs),.combine='rbind') %do%{
  if(names(altDirs)[alt] != "Measured"){
    w2i_alt <- LoadAltW2npts(file.path(altDirs[[alt]][['fld']],
                                       altDirs[[alt]][['RW2nptsFlNm']])) 
    w2i_alt$Alt <- names(altDirs)[alt]
    return(w2i_alt)
  }
}

if(any(grepl('Meas',names(altDirs)))){
  WSELVmeas <- ReadMeasWSELVs()
}

RuleCurveDir <- file.path(RefDataDir,'rule_curves')
rcs <- ReadRuleCurves(RuleCurveDir) %>% 
  expand_grid(Year = c('2011','2015', '2016'),
                     Alt = names(altDirs)) %>%
  mutate(Year = factor(Year,levels = levels(w2npts$Year)),
         Site = factor(Site,levels = levels(w2npts$Site),ordered=T)) 

w2npts <- w2npts %>% bind_rows(rcs) %>%
  mutate(Param = as.factor(Param))

# Plot Comparison of Alts
CompareAltW2npts()
  
  
```


```{r GetTDGdata, echo=F}
#Read summary of Ops and TDG data
#source(file.path(dataDir,'WVEIS_functions_2021-10-04.r'))
#source('C:/Users/g2echnb9/Documents/WillametteEIS/RES-OPS/WVEIS_functions_2021-10-04.r')
source(file.path(dataDir,'WVWQfunctions.r'))

tdgOpsSum <- ReadAltTDG('TDGsum')
tdgExcYr <- ReadAltTDG(var = 'TDGsumExcByYr')
tdgExcMD <- ReadAltTDG('TDGsumExcByMD')
tdgAll <- ReadAltTDG('tdg4altcmp')
# Generate comparison plots of TDG

CompareAltTDG()
```

Get W2 file output. Load RData file for an example.

```{r GetW2Temp, echo=F, message = FALSE}
#Read summary of Ops and TDG data
source(file.path(dataDir,'WVWQfunctions.r'))
#source('C:/Users/g2echnb9/Documents/WillametteEIS/RES-OPS/WVEIS_functions_2023-02-04.r')
Tmeas <- ReadMeasTemps()
#source(file.path(dataDir,'get.w2.inflows.r'))

# If you can't get the following line of code to run, try just loading the example in the RDATA file.
ReadAltW2Res(fldrs = na.omit(sapply(altDirs,function(x){x[['w2dir']]})))
CalcTTdifs()

for(tt in c('RA','W2','TMDL','ORStnd')){
  # Plot time-series difference from target
  PlotW2TempByYear(ttType = tt)
  MakeTimpacts(ttType = tt)
  #save.image(file = file.path(dataDir,"WVEIS_Rscripts4WQpostprocessing/WVEIS_WQCompareNAAtoAlt5_2022-08-10.RData"))
  #load(file.path(dataDir,"WVEIS_Rscripts4WQpostprocessing",'WVEIS_WQCompareNAAwMeasurements_2022-03-16.Rdata'))

  #TtDifYr %>% filter(LifeStage == 'MarMay',Location == 'GPRO',Year == '2015')
  #TtargDifLoc %>% filter(Location == 'CGR',Year == '2015',Alt =='Alt2b',TargNm =='ORStnd')
  # This will plot the various summary graphs and tables of the W2 modeling
  #if(grepl('W2|ORStnd',tt)){
    ComparePlotAltW2(ttType = tt)
  #}
}

```
